Sketch of DP - Bayesian Inference

### 2018-07-16 main-sketch.tex
typo

@@

\section{Baseline Approach - Laplace Mechanism}
\label{sec_lap}
Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy. They perturbed the parameter updates of $\betad$ distribution from Bayesian inference and truncated to rule out invalid $\betad$ parameters to get the protected posteriors. Furthermore, we extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d. Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way. 
%where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
The private posterior is $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.

>>>>

where $+$ denotes the 

@@

% \section{Baseline Approach - Laplace Mechanism}
% \label{sec_lap}
% Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy. They perturbed the parameter updates of $\betad$ distribution from Bayesian inference and truncated to rule out invalid $\betad$ parameters to get the protected posteriors. Furthermore, we extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d. Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way. 
% %where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
% The private posterior is $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.
